Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-09-06 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   modified:   picture/picture4.key   modified:   picture/picture4.pdf

\def\year{2021}\relax
%File: formatting-instructions-latex-2021.tex
%release 2021.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
\pdfinfo{
  /Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
  /Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen, Francisco Cruz, Marc Pujol-Gonzalez)
  /TemplateVersion (2021.1)
}

\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage{spconf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint training of classification model and similarity model for low-resource
  text classification in chatbot
}

\author{
  %Authors
  % All authors must be in the same font size and format.
  Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
  AAAI Style Contributions by Pater Patel Schneider,
  Sunil Issar,  \\
  J. Scott Penberthy,
  George Ferguson,
  Hans Guesgen,
  Francisco Cruz,
  Marc Pujol-Gonzalez
  \\
}
\affiliations{
  %Afiliations

  \textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
  %If you have multiple authors and multiple affiliations
  % use superscripts in text and roman font to identify them.
  %For example,

  % Sunil Issar, \textsuperscript{\rm 2}
  % J. Scott Penberthy, \textsuperscript{\rm 3}
  % George Ferguson,\textsuperscript{\rm 4}
  % Hans Guesgen, \textsuperscript{\rm 5}.
  % Note that the comma should be placed BEFORE the superscript for optimum readability

  2275 East Bayshore Road, Suite 160\\
  Palo Alto, California 94303\\
  % email address must be in roman text type, not monospace or sans serif
  publications21@aaai.org

  % See more examples next
}

>>>>

\def\year{2021}\relax
%File: formatting-instructions-latex-2021.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage{spconf}
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT

\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
\pdfinfo{
  /title (Joint training of classification model and similarity model for
  low-resource text classification in chatbot)
  /Author (no author informmation)
  /TemplateVersion (2021.1)
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint training of classification model and similarity model for low-resource
  text classification in chatbot
}
